Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-02-05 paper.tex
fix: typo
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

U Cephei is a very interesting binary star system and a great pick to try catching transit eclipses.

@@

First of all U Cephei period is 2.493 days, which is quite short and allows for multiple chances to observe it on a short period of time. 
Even though this period seems short since it is not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
Making observation nights possible every 5 days.
Considering the fact weather conditions are critical for this field, managing to have a night with good seeing condition can also be a challenge, so having multiple chances to observe the same system is a great advantage.

>>>>

U Cephei is a very interesting binary star system and a great pick to try catching transit eclipses for multiple reasons

@@

First of all U Cephei period is 2.493 days \cite{VariableStar}, which is quite short and allows for multiple chances to observe it on a short period of time. 
Even though this period seems short since it is not exactly 3 days but 2 and a half it means that one observation out of 2 will be at night and the other during the day.
Making observation nights possible every 5 days.
Considering the fact weather conditions are critical for this field, managing to have a night with good seeing condition can also be a challenge, so having multiple chances to observe the same system is a great advantage.
